\section{Pricing and Selling of Goods}
\label{sec:pricing_mechanics}

Part of the production simulation is the product view. Here the player can get an overview about the costs of every single component. Also, he or she can define the market price for selling and the quantity to produce there.

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
 Products & \begin{tabular}{@{}c@{}}Qty to \\ Produce\end{tabular} & \begin{tabular}{@{}c@{}}Amount \\ in Stock\end{tabular} & \begin{tabular}{@{}c@{}}Cumulated Com- \\ ponent Costs\end{tabular} & \begin{tabular}{@{}c@{}}Price for \\ Market (Sell)\end{tabular} & \begin{tabular}{@{}c@{}}Profit \\ Margin\end{tabular} \\ \hline
 Product A &  & 12 & 332,56 & 599,99 & 47.8\% \\ \hline
 Product B &  & 554 & 62,05 &   & - \\  \hline
 Product C &  & - & 164,67 &   & -\\ \hline
\end{tabular}
\caption{xxxxxx}
\label{table:xxxx}
\end{table}

The first column, "Product" displays the name of a product, that the player when he or she chose the product portfolio. The number of rows depends on the number of products the player added to the product portfolio. 
The "Qty to Produce" field is an input field where the player can type in an integer value. If the amount entered is larger than the cumulated sum of overall machinery capacity, then the player sees the error message: "Your machinery capacity is not sufficient. Either produce a smaller amount or buy new machinery". This is calculated as follows:

\begin{equation}
   If entered amount \geqslant asdfasdfasdfasdfasdfasdf sum of overall machinery capacity LIVJA
\end{equation}
TOTAL warehouse capacity (nwh * cwh) \ref{warehouse_simulation} - total number of products stored
Amount in stock - JANINE – do we have such thing? Wenn nicht, dann concept aber derzeit nicht in prototype. \\
Cumulated Product Costs - per product, includes the xxxxxx (component prices) plus – LIVJA???\\
Price for market (sell) - input field where player can type in a price (with two decimals) in CapCoins. \\
Profit margin - \begin{equation}
    Profit margin = \frac{Price for Market (Sell) - Cumulated Component Costs}{Price for Market (Sell)} * 100
\end{equation}
