\subsection{Product Support}  \label{product_support_simulation}

%\gls{cST}  % costSupportType
%\gls{tSTQ}  % totalSupportTypeQuality
%\gls{tSQ}  % totalSupportQuality
%\gls{qSP}  % qualitySupportPartner
%\gls{tSC}  % totalSupportCost
%\gls{cSP}  % costSupportPartner

%Janine
In addition to the product itself, a product support strategy is also necessary. This strategy should not only consist of maintaining the actual product functionality, but should also include further services for the customer in order to provide him with the greatest possible value with his product. [REFERENCE: Design and development of product support and maintenance concepts for industrial systems] Additional services could for example be a mobile app or and actively managed community.  
In Capitalism X, the player is offered various options how he wishes to design the product support for his products. Table \ref{Support_types} shows the different services he can purchase from an external partner, how they influence the overall product support of the company and the monthly cost (\gls{cST}). The variants can be combined by the player as desired. If no option is selected, this automatically means that no support is offered.
Before the company can offer product support to its customers, the player must hire an external support partner. Basically only one partner can be hired at a time, but he can be fired at any time.

\begin{table}[ht]
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Support type & Influence on the product support & monthly cost \\
    No product support   & -10   & 0    \\
    Online self service  & 0     & 50   \\
    Online support       & 20    & 100  \\
    Telephone support    & 30    & 250  \\
    Store support        & 40    & 400  \\
    Additional services  & 10    & 50   \\     
    \hline
    \end{tabular}
    \caption{Support type influence and costs}
    \label{Support_types}
\end{table}

The total support type quality (\gls{tSTQ}) is calculated from the various support types offered; this is simply the sum of the support types. The quality of the total product support (\gls{tSQ}) of the company is influenced not only by the offered support types but also by the dedicated support company, more precisely its quality (\gls{qSP}). The calculation is done as follows:
\begin{equation}
\label{func:totalProductSupport}
\begin{aligned}
    if ( qSP ≤ 50 ) tSQ = { 0,4 *qSP + 0,6 * tSTQ } \\
    else tSQ = { 0,3 * qSP + 0,7 * tSTQ }
\end{aligned}
\end{equation}

The total cost of product support (\gls{tSC}) is calculated from the monthly cost of the support types offered and the general monthly cost (\gls{cSP}) for cooperation with the partner company.
\begin{equation}
\label{func:totalSupportCost}
    tSC = sum (cST) + cSP
\end{equation}